%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{xcolor}
\usepackage[none]{hyphenat}
\usepackage{changepage}


\begin{document}

\header{Steven}{Hall}{Software Engineer} % Your name and current job title/field

%-------------------------------------------------------------------------------
%  SIDEBAR SECTION
%-------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
\href{mailto:steven@stmhall.ca}{steven@stmhall.ca}
\href{http://github.com/hallzy}{GitHub: hallzy}
\href{https://www.linkedin.com/in/steventmhall}{LinkedIn: steventmhall}
\section{Languages}
Bash Script
C/ C++
HTML/ CSS
Java
JavaScript/ AJAX/ JQuery
TypeScript
MySQL/ PostgreSQL
PHP
Python
VimScript
\section{Computers and Programs}
Git/ SVN
Linux (CLI proficient)
Vim
\end{aside}

%-------------------------------------------------------------------------------
% Work Experience
%-------------------------------------------------------------------------------
\section{Work Experience}

\begin{entrylistSkinny}

\entrySkinny
{April 2018--May 2020}
{LinuxMagic Inc. {\normalfont Full Stack Web Developer}}
% {Vancouver, BC}
{
\begin{itemize}
\item Worked on feature enhancements, customer requests, and bug fixes for
MagicMail, a carrier grade email platform for ISPs and Telcos using a
proprietary PHP MVC, PostgeSQL, Bootstrap, and JQuery.
\item Worked on feature enhancements and bug fixes for other systems including
the  CRM, sales system, and other product websites (MagicSpam, SpamRats) using
CakePHP, MySQL and PostgreSQL, JQuery, Bootstrap, and a proprietary PHP MVC.
\item Migrated the sales system database from an Oracle to PostgreSQL
\item Led a project to redesign and rewrite the SpamRATS product website from
the ground up using a proprietary PHP MVC, Bootstrap, JQuery, and
PostgreSQL.
\item Completed work orders for customers by communicating directly with the
customer and performing their development work in a timely and professional
manner using a proprietary PHP MVC, JQuery, and MySQL
\item Mentored new Web Developer hires.
\item {\bf Skills}: Proprietary PHP MVC Framework, CakePHP, CSS, JavaScript,
 JQuery, Bootstrap, MySQL, PostgreSQL, Bash, SVN, HTML\\
\end{itemize}
}
\entrySkinny
{May 2016--Aug 2016}
{UBC {\normalfont Big Data Research Assistant}}
% {Vancouver, BC}
{
\begin{itemize}
  \item Goal: To share memory (RDDs) across Apache Spark instances through a
  unified memory manager.
  \item {\bf Skills}: Scala, Python, Hadoop, Apache Spark, Git, Bash\\
\end{itemize}
}
\entrySkinny
{Jan 2015--Aug 2015}
{Ericsson Canada Inc {\normalfont Software Developer Intern}}
% {Burnaby, BC}
{
\begin{itemize}
  \item Tested and developed QoS and PBR software solutions on a variety of
    Ericsson's enterprise scale routing platforms using manual router
    configurations and Perl scripts for testing.
  \item Presented demos showing the functionality and progress of policy-based
  routing during the testing and development phases.
  \item {\bf Skills}: C, Perl, Git, CVS, Bash
\end{itemize}
}
% \entrySkinny
% {Summer 2014}
% {ByteCom Computer Services {\normalfont Computer Repair Technician}}
% % {Surrey, BC}
% {
% \begin{itemize}
% \item Repaired broken, slow, and non-responsive computers in a computer repair
% shop by replicating the customer’s problem, identifying the cause of the
% problem, and repairing the problem with the tools we had, resulting in satisfied
% customers.
% \item Techniques used to repair the computers include file and registry
% manipulations, and taking the computers apart to diagnose hardware problems,
% resulting in faster, and better working computers.
% \end{itemize}
% }
\end{entrylistSkinny}

%-------------------------------------------------------------------------------
%  Technical Projects
%-------------------------------------------------------------------------------
\begin{entrylist}

\section{Technical Projects}

\entry
{Aug 2020}
{NES Tetris Web Clone}
% {}
{
\begin{itemize}
\item Goal: To make a web based Tetris game that mimics the behaviour and rules
of the classic NES Tetris game as closely as possible, with the ability to send
a unique URL to a friend so that they are able to play the same sequence of
pieces so you can compare your scores. The scores would be listed on the page
for that game.
\item Currently the game is in development. The game itself is playable but
there are some bugs and issues I plan to address, and scores for the game are
not saved or listed on the page. I plan to solve this by saving scores to a
database, and using PHP to generate the game page with the scores listed.
\item {\bf Skills}: TypeScript, PHP, PostgreSQL, HTML, CSS\\
\end{itemize}
}
\entry
{May 2020}
{TV Show Notification and Calendar}
% {}
{
\begin{itemize}
\item Created a Google App Script that retrieves air dates for episodes of TV
Shows that I watch. The script uses that information to figure out what episodes
I don't have in my Google Calendar already and will automatically add them for
me.
\item {\bf Skills}: Google App Script, TypeScript\\
\end{itemize}
}
\entry
{Nov 2017}
{Online Web Store}
% {}
{
\begin{itemize}
\item Built a web application that mimics an online store using AJAX requests
and MongoDB.
\item Resulted in a functioning webpage that received a high grade.
\item {\bf Skills}: JavaScript, HTML, CSS, MongoDB\\
\end{itemize}
}
\entry
{April 2014}
{Electromagnetically Tethered Robot}
% {}
{
\begin{itemize}
\item Programmed a custom built autonomous robot to follow an electromagnetic
signal. I also programmed the custom built remote that created this EM signal.
\item The remote could also send binary data through the magnetic field to tell
the robot to perform certain manoeuvres such as spin 180 degrees, move back and
forth, and parallel park.
\item Resulted in a fully functioning robot and a high project grade.
\item {\bf Skills}: C (Embedded)\\
\end{itemize}
}
\end{entrylist}

% \newpage
% \newgeometry{top=1.5cm,bottom=1.5cm,right=1.5cm,left=1.5cm}

%-------------------------------------------------------------------------------
%  Other Work Experience
%-------------------------------------------------------------------------------
% \section{Other Work Experience}

% \begin{entrylistSkinny}


% \end{entrylistSkinny}

%-------------------------------------------------------------------------------
%  Volunteer Experience
%-------------------------------------------------------------------------------
% \section{Volunteer Experience}

% \begin{entrylistSkinny}

% \entry
% {2010--2013}
% {North Delta Baseball Association and Surrey Canadian Baseball Association {\normalfont Assistant Coach}}
% % {North Delta, BC and Surrey, BC}
% {
% \begin{itemize}
% \item Coached range of age groups over a three season period.
% \item Duties include teaching proper throwing and hitting mechanics, resulting
%   in increased performance by every player.
% \end{itemize}
% }
% \end{entrylistSkinny}

%-------------------------------------------------------------------------------
%  EDUCATION SECTION
%-------------------------------------------------------------------------------
\begin{entrylist}

\section{Education}

%------------------------------------------------
\entry
{2013--Dec 2017}
{University of British Columbia {\normalfont Vancouver, BC}}
% {Vancouver, BC}
{\\Bachelor of Applied Science in Computer Engineering (Software Option)}
%------------------------------------------------
\entry
{2012--2013}
  {Kwantlen Polytechnic University {\normalfont Surrey, BC}} % {\normalfont of IT}}
% {Surrey, BC}
{\\Engineering Certificate}
\end{entrylist}

% \newpage

%-------------------------------------------------------------------------------
%  AWARDS SECTION
%-------------------------------------------------------------------------------

%\section{Awards}

%\begin{entrylistSkinny}
%%------------------------------------------------
%\entry
%{2012}
%{Coaching Staff of the Year (Highest voted coaching staff in the league)}
%{}
%{Surrey Canadian Baseball Association}
%%------------------------------------------------
%\end{entrylistSkinny}

%-------------------------------------------------------------------------------
%  INTERESTS SECTION
%-------------------------------------------------------------------------------
\begin{entrylist}

\section{Interests and Activities}

\interest
{
\begin{itemize}
\item Programming and computers
\item I love to learn and figure out how things work
\item Contributing to open source projects such as:
  \begin{itemize}
    \item Gravity programming language
    \item Git Radar
    \item Various Vim plugins
  \end{itemize}
\item Suckless Software - I use a lot of Suckless software on my personal
 computer including:
  \begin{itemize}
    \item DWM
    \item dmenu
    \item sent
    \item st
    \item sxiv
  \end{itemize}
\item Encryption
\item Computer and information security
\item Network security including router configuration and VPNs.
\item Configuring my Vim text editor so that it now has over 175,000 lines of
additional configuration code and plugins which increases my productivity when
coding and editing text.
\item I perform all of my own car repairs and maintenance including:
\item Skiing, Snowboarding
\item Baseball, Hockey, Lacrosse
\end{itemize}
}
\end{entrylist}

% % Software Specific
% \keyword
% {
% Agile
% Applications
% ASP.NET
% Build
% C\#
% Code
% Collaborate
% Data
% Design
% Development
% Engineering
% Environment
% Java
% JavaScript
% Knowledge
% Mobile
% .NET
% Product
% Projects
% Software
% Solutions
% SQL
% Team
% Technologies
% Testing
% Tools
% Web
% % General
% accommodated
% accomplished
% achieved
% acquainted
% activated
% active
% adaptable
% adapted
% administered
% teamwork
% review
% advertised
% advised
% advocated
% aggressive
% aided
% alert
% altered
% ambitious
% analytical
% analyzed
% applied
% appraised
% approved
% arranged
% assembled
% eager
% excited
% exciting
% assigned
% assisted
% assumed
% attached
% attained
% attentive
% augmented
% authorized
% balanced
% bought
% broad-minded
% budgeted
% built
% chaired
% classified
% collected
% combined
% commanded
% communicated
% completed
% condensed
% conducted
% conferred
% conscientious
% consistent
% consolidated
% constructive
% consulted
% controlled
% converted
% coordinated
% counselled
% created
% creative
% curtained
% delivered
% demonstrated
% dependable
% designated
% designed
% determined
% developed
% devised
% diagnosed
% diplomatic
% directed
% disciplined
% disclosed
% discontinued
% discovered
% discrete
% dispatched
% displayed
% drafted
% economical
% economized
% edited
% educated
% efficient
% eliminated
% employed
% encouraged
% endorsed
% energetic
% enterprising
% enthusiastic
% established
% estimated
% evaluated
% examined
% exchanged
% executed
% exhibited
% expanded
% expedited
% extended
% extroverted
% facilitated
% fair
% familiarized
% forceful
% formulated
% founded
% fun
% funny
% governed
% grouped
% guaranteed
% guided
% handled
% hard working
% hard-working
% headed
% hired
% humor
% humorous
% humour
% humourous
% illustrated
% imaginative
% implemented
% improved
% increased
% independent
% influenced
% informed
% initiated
% innovated
% installed
% instituted
% instructed
% interpreted
% introduced
% inventoried
% invested
% investigated
% lectured
% logical
% loyal
% maintained
% managed
% mapped
% mature
% maximized
% measured
% merged
% methodical
% minimized
% modernized
% modified
% motivated
% negotiated
% notified
% objective
% observed
% obtained
% operated
% optimistic
% organized
% perceptive
% perfected
% personable
% planned
% pleasant
% positive
% practical
% prepared
% prescribed
% procured
% produced
% productive
% projected
% promoted
% publicized
% published
% realistic
% recommended
% rectified
% reduced
% regulated
% reliable
% relocated
% removed
% reorganized
% repaired
% replaced
% reported
% resolved
% resourceful
% respective
% restored
% revised
% scheduled
% self-reliant
% sense of humor
% sense of humour
% serviced
% simplified
% sincere
% solved
% sophisticated
% sponsored
% stabilized
% strengthened
% studied
% suggested
% supervised
% supplemented
% surpassed
% systematic
% tactful
% talented
% taught
% terminated
% transferred
% transformed
% travel
% unified
% updated
% utilized
% verified
% vetoed
% will
% }

\newpage

\end{document}
